\documentclass{article}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{hyperref}

\title{Appendix 1: Test Cases Classification}
\author{}
\date{}

\begin{document}

\maketitle

\begin{longtable}{p{0.5cm}p{6cm}p{2cm}p{3cm}p{2.5cm}}
\caption{Test Cases Classification} \\
\toprule
No. & Query & Complexity & Domain & Interaction Type \\
\midrule
\endfirsthead

\multicolumn{5}{c}%
{{\bfseries Table \thetable{} -- continued from previous page}} \\
\toprule
No. & Query & Complexity & Domain & Interaction Type \\
\midrule
\endhead

\midrule
\multicolumn{5}{r}{{Continued on next page}} \\
\endfoot

\bottomrule
\endlastfoot

1 & What is the total fuel cost for ferry Jupiter in January 2024 assuming that the price per liter is 20 sek? & Simple & Fuel Efficiency & Retrieval \\
2 & What is the average speed of ferry Jupiter? (in km/h) & Simple & Route Optimization/Operations & Retrieval \\
3 & How many vehicles are on average left at the terminal for inbound trips? & Moderate & Route Optimization/Operations & Aggregation \\
4 & How many vehicles are on average unable to board (left behind at the terminal) per trip for ferry Jupiter during summer months (6, 7, 8)? & Complex & Route Optimization/Operations & Aggregation \\
5 & What is the highest average daily PCE (Passenger Car Equivalent) value for Furusundsleden route? (outbound and inbound combined)? & Complex & Route Optimization/Operations & Aggregation \\
6 & What is the average distance travelled on Ljusteröleden (in nautical miles)? & Simple & Route Optimization/Operations & Retrieval \\
7 & What is the total Passenger Car Equivalent (PCE) during the peak hour for route Aspöleden in February, combining both outbound and inbound directions? & Complex & Route Optimization/Operations & Aggregation \\
8 & What is the average fuel consumption on the route Ljusterö to Östanå, combining both outbound and inbound? & Moderate & Fuel Efficiency & Aggregation \\
9 & What is the average trip duration for Oxdjupsleden (in minutes)? & Simple & Route Optimization/Operations & Retrieval \\
10 & What is the fuel consumption (liters per nautical mile) for ferry Merkurius? & Simple & Fuel Efficiency & Retrieval \\
11 & What is the average utilization percentage for Oxdjupsleden (average PCE vs the ferry's maximum capacity)? & Complex & Route Optimization/Operations & Aggregation \\
12 & What's the average number of vehicles left at terminals in June for Furusundsleden (combine outbound and inboud)? & Moderate & Route Optimization/Operations & Aggregation \\
13 & What is the average daily vehicle throughput per day for Vaxholmsleden (only outbound)? & Moderate & Route Optimization/Operations & Aggregation \\
14 & What's the average PCE for Oxdjupsleden on Thursdays (calculated as the mean of the average inbound PCE and average outbound PCE)? & Moderate & Route Optimization/Operations & Aggregation \\
15 & Which hour of the day has the highest average passenger car equivalent (PCE) for route Ljusteröleden (with inbound and outbound trips combined)? & Moderate & Route Optimization/Operations & Aggregation \\
16 & What is the average passenger car equivalent (PCE) during June, July, August for Vaxholmsleden route (calculated as the mean of the average inbound PCE and average outbound PCE)? & Moderate & Route Optimization/Operations & Aggregation \\
17 & What is the difference in percent of pedestrians to vehicles, comparing weekdays to weekends for Vaxholmsleden? & Moderate & Route Optimization/Operations & Comparison \\
18 & At which hour does Oxdjupsleden on average have the highest passenger car equivalent (PCE)? & Moderate & Route Optimization/Operations & Aggregation \\
19 & What was Aspöleden's ratio of pedestrians to vehicles in 2023? & Moderate & Route Optimization/Operations & Aggregation \\
20 & What is the total CO2 emission from Ljusteröleden in February 2024, assuming 2.68 kg CO2 per liter of fuel? & Moderate & Environmental Impact & Aggregation \\

\end{longtable}

\end{document} 